% !TEX root=../thesis.tex

\chapter{Background}
\label{chapter:background}

A train network is a complex system. Almost every running train have the 
possibility to affect almost every other train running in the system.  When 
you look at a busy area, such as a major city and it's closest
area, a great deal of trains can be on the move at any given time on a
railway network with limited capacity. This leads to limited time slots for each 
train and every problem can lead to major delays.


Even though one train may be experiencing delay, this delay may be part of a
sequence of problems that can be tracked back to a seemingly unrelated part of
the the network and a perhaps a bad decision there\cite{cule2011mining}. \\

In the Norwegian railroad a train is on schedule if it arrives the final
destination within a margin on 3 minutes and 59 seconds, if it is a long
distance train the margin is 5 minutes and 59 seconds. 
Jernbaneverket (see\vref{sub:subsection_jernbaneverket}) defines regularity as the number of trains that gets run as 
planed in the time schedule. 
Uptime in regards to punctuality is defined by Jernbaneverket from the hours of delay\footnote{Hours of delay due to infrastructure excluded traffic	management and external conditions} caused by infrastructure relative to sum of planed train hours\footnote{Planed train hours (passenger and freight trains)} per year.
\cite{jernbaneverketPunklighetsTall}
\begin{equation} Uptime =
		\frac
				{
					\text{Train hours - Hours of delay}
				}
				{
					\text{Train hours}
				}\times 100 
\end{equation}\\

As Landex\cite{landex2009gis} says, there exist few GIS-approaches concerning
visualization of railroad capacity. Both the visualizations shown by Landex and
in section \vref{sect:backgroundExamples} only seems to take into consideration if
the trains are delayed, and the amount of delay. 

However, to minimize the delays all over the railway network, it may be necessary
to not only see that certain routes are delayed but also why it is delayed. To
be able to understand this, you need to be able to mine data from the railway
network administrator and have a good visualization tool to present it. 

\pagebreak
\input{parts/background_parts/examples}
\input{parts/background_parts/frameworks}
