% !TEX root=../thesis.tex
\chapter{Conclusion and Future work}
\label{chapter:conclusion}

\section{Conclusion} % (fold)
\label{sec:conclusion}
To have a system that are capable of awareness of stakeholder and their needs
to aggregate over a rich set of data, it is important to both have a clearly
defined stakeholders with their requirements and needs, data sets which are 
adapted to the stakeholders, and aggregation methods which fit the 
stakeholders needs and the data sets. 

We have created a prototype to help define important characteristics for a
system that are aware of the stakeholder and their needs when processing data,
by the use of the Design Science Research Process. To properly define the 
stakeholders, their needs, and their areas of responsibility in a hierarchy is 
crucial, as everything is based on the stakeholders and their needs and 
requirements. The system is able to fetch data according to the needs of the 
current stakeholder and processes the data according to their step in the
hierarchy, by being able to navigate through the hierarchy. \\

In order to have the ability to navigate the hierarchy and process the data 
accordingly, the areas of responsibility should be stored in the hierarchy for 
enabling the system to find the compatible data with the areas. The different
data sets should be stored in a structure that enables a dynamic link to the
hierarchy. We proposed a semi-distributed databases, where the hierarchy is
stored in a database and the other data sets connected to the stakeholder
through the hierarchy database. The database structure proposed does demand
that the data sets are processed to a similar structure, and merged to a
consistent definition of data fields. 

Use of the hierarchy based areas of responsibility is important, to aggregate 
the data sets according the stakeholders and their requirements. The 
aggregation method should be specified in the requirements for each 
information type, as each data set can be different and/or the stakeholders 
have a different need for that information.

The system should be able to use the visual presentation of the data to limit
the visualization to the current stakeholder, by use of the area of
responsibility of the current stakeholder.\\

In order for a system to provide stakeholder awareness, the domain it shall 
operate within needs to defined. The stakeholders the system shall provide 
awareness for, must be defined within the domain along with their 
requirements, needs, and areas of responsibility. When the stakeholders have
been defined within the domain, they need to be organized in a aggregatable 
structure for the system to process and present the data according to the
stakeholders requirements. We demonstrated this by defining the stakeholders
within a railway domain in a hierarchy based on their areas of responsibility.
The hierarchy enabled us to aggregate the data according to the active
stakeholder, both when processing and presenting the data.

\section{Future work} % (fold)
\label{sec:future_work}
In this section we describe areas found during the work of this thesis in 
which there are a possibility for future work. \\

The most obvious work that can be done, is to test the system against users.
One can observe how the users thinks the system takes the stakeholders 
requirements and needs into consideration, by testing the system with users.
The observations can then be used in the process loop described in 
\Ref{cha:research_questions_and_method} \nameref{cha:research_questions_and_method}
to redefine the objectives of the solution. \\

As the system presented in this thesis uses historical data, a further
expansion would be to test the system with live data. Measuring of the affect
aggregated data have when users analyze the data in order to improve safety and
punctuality, can be done when looking at current data. \\

A further way of improving awareness could be to expand the system by
presenting more types of data, in order to take into consideration more of the 
different stakeholders needs. Presenting more data sets was discussed in the 
two workshops held(see \Ref{sec:workshop_2014_04_04} and \Ref{sec:workshop_2014_04_24}).

% section future_work (end)

%\input{parts/conclussion_parts/characteristics}

