\addcontentsline{toc}{section}{Preface}
\section*{Preface}

We originally chose this project because we envisioned being able to create a
state of the art driver information system. With this report we have come a bit
closer to the realization of such a system. 

During the work on the project we have studied a lot of literature pertaining
to both technology and architecture design, and we feel that we have learned a
lot about both. 

We do acknowledge that at times the process has been moving
very slowly, a lot of notes were scribbled down, but took its time to
materialize into the report and supporting documents. The methodological
approach to the architecture development has been inspired from Craig Larman's
descriptions of the ``Unified Process'', but with a selective approach to
artifacts utilized -- concentrated on the ones that seemed most beneficial.
Some of the artifacts attached are rather bare and lacks a bit of structure. We
do not consider any of artifacts complete as system development should be
performed as an iterative process, refining everything along the way.

We wish to thank our project supervisor, Hallvard Trætteberg, for his patience
with us in times when results were marginal, and pushing us in the right 
direction when we needed it. We hope that this final
report goes some way in delivering what we originally set out to do.


\mbox{}\\[10pc]
\begin{center}
Trondheim, December 16, 2013\\[1pc]
\vspace{15 mm}
Magnus Bae ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ Magnus Krane
\end{center}

\clearpage
