% !TEX root=../document.tex

\section{Product overview}

\subsection{Product Perspective}

Placeholder text. 
Also, insert system context diagram.

\subsection{Summary of Benefits}

\begin{tabularx}{\textwidth}{|X|X|}
	\hline
	\rowcolor{gray!50}
	Supporting Feature & Stakeholder Benefit \\
	\hline
	Functionally, the system will provide all the common functionality of a
	traditional dashboard, including speedometer and warning indicators.
		&
		Increased availability of information for the driver. \\
	\hline
	Support for receiving messages over wireless link.
		&
		Allows for giving messages without using radio-communication. \\
	\hline
	Real-time processing and evaluation of sensor data.
		&
		Ensures that system has comparable response times of traditional static
		systems \\
	\hline
	Support for event-driven display of information.
		&
		Less intrusive interface that results in fewer distractions.\\
	\hline
	Configurable message formats, sensor setups, and display configurations.
		& 
		Gives a very flexible system that is portable and allows for reuse of
		high-level components.\\
	\hline
	Externally configurable with support for upload of stored configurations and
	ability to create configurations while not connected
		&
		Gives a flexible way of configuring without requiring access to the vehicle
		for long periods. \\
	\hline
	Support for aggregation of data from sensors and triggered display
		&
		Allows for showing information when it is relevant, creating less noise at
		other times. \\
	\hline
\end{tabularx}

\subsection{Assumptions and Dependencies}
The realization of the system depends on the availability of a heads-up display
of some sort. Without this component the system can not be realized. For
purchasing components there is a dependency on funds, which hopefully will
stem from sponsors co-operating with Revolve NTNU. 

\subsection{Cost and Pricing}
The prices of solutions for realizing a functional system ranges from USD 200
and up to USD 5,000 for the most costly solutions. 

\section{Summary of System Features}
The system under discussion is an advanced Heads-Up Display replacing a 
traditional dashboard-type instrumentation with a wide feature set:
\begin{itemize}
	\item Aggregation of data and event-driven display updates.
	\item Real-time processing and display of data.
	\item Wireless reception of messages with duplex communication.
	\item Flexible configuration possibilities.
	\item Remote configuration capability.
	\item Stored configurations.
	\item Portable architecture.
	\item High-level support of various network
	standards.
\end{itemize}
