% !TEX root=../thesis.tex
\chapter{System requirements}
\label{requirements}

In this chapter we present the requirements for a driver information system for Revolve NTNU.

\section{Non-functional requirements} %they're also non-fictional.

The system
\begin{itemize}
	\item Shall deliver information to the driver with less than 200 ms delay 90\% of the time.
	\item Shall not negatively affect the drivers performance.
	\item Shall not obstruct the drivers entry or exit from the vehicle.
	\item Shall connect to the car's CAN-bus system.
	\item Shall not interfere with the normal operating of the car's CAN-bus system.
	\item Shall convert received sensor values to real-world values.
	\item Shall help Revolve NTNU obtain their goals in the FS competitions.
	\item Shall support easy removal or addition of new sensors and equipment
\end{itemize}

\section{Functional requirements} %These are fictional
The system
\begin{itemize}
	\item Shall not deliver old information in the case of loss of one or more inputs.
	\item Shall deliver information about the current speed.
	\item Shall deliver information about the current battery charge level.
	\item Shall warn if the current battery charge level is running below critical threshold\footnotemark[1].
	\item Shall warn and alert if the battery temperature has passed a critical threshold\footnotemark[1].
	\item Shall deliver information about lap times after lap is completed if lap-timing system is operational.
\end{itemize}

%footnotes
\footnotetext[1]{This value is unknown at the time of writing and will be defined at a later point}
