% !TEX root=../thesis.tex

\chapter{Theory}

In this appendix we look at --- meh!

\subsection{Types of systems}
In general there are basically two types of driver information systems, Heads Down Display and Heads Up Display. 
The first is represented by the classic we all know; the dashboard. The second we find in more advanced 
applications such as in fighter planes where the pilot wears a helmet with a display in the visor. In the latter 
example the operator has a display that is fixed in position, but because the helmet moves with head movement, so does
the display. In the first example the display is fixed and operator head and eye movement is required to use the display during normal
operation.

Revolve have always chosen to utilize dashboard-based information systems. Mainly consisting of LED-displays and 
LED-indicators. To get an insight into the efficiency of these systems we conducted an interview with a driver 
from the 2013-competitions. During this interview we learned that during a race it is very hard to consume
information from the dashboard. The course twists and turns, and requires the driver to focus on track and on handling the car; braking and 
acceleration. This makes it difficult for the driver to shift focus down to the dashboard and usually requires longer straight sections of
track to be able to gather any meaningful information.



% \subsection{Scope}
% The scope of this project is to research the state-of-the-art of 
% HUD-technology. What type of devices and technology that can 
% be leveraged to create a prototype HUD for application in a racing car. 
% Focusing both on the racing parts of the competition, and on helping
% to win points in the business side of the competition. (link to background chapters)

% \subsection{Application}Incorporating a HUD-system in a race car is something that could provide a competetive advantage. For Revolve NTNU 
% this is doubly so, since the Formula Student competetion covers so many disiplines the advantages given may also contribute to better 
% results in business-class competitions. (link to background chapter here)
